miniKanren with fair search strategies

### 2019-05-18 Paper/paper.tex
fix typo in DFSbi

Balanced interleaving DFS (DFS$_\textrm{bi}$) has almost-fair \disj{} and unfair 
\conj{}. The implementation of DFS$_\textrm{bi}$ differs from DFS$_\textrm{i}$ 
in the \disj{} macro. We list the new \disj{} with its helper in 
Fig.~\ref{balanced-disj}. The helper \code{disj+} builds a balanced binary tree 
whose leaves are the goals and whose nodes are \code{disj2}, hence the name of 
this search strategy. The first argument 
to \code{disj+} is the goals. And the next two arguments accumulate goals in 
the left and right subtrees. The first clause says that when there is one goal, 
the tree is the goal itself. When there is more goals, they are partitioned 
into two sub-lists. The partition is done by repetitively dispatch the first 
two goals (the last clause), until no goal remains (the second clause) or one 
goal remains (the third clause). In contrast, the \disj{} in DFS$_\textrm{i}$ 
constructs the binary tree with the same collection of leaf nodes but in a 
particularly unbalanced form.

>>>>

Balanced interleaving DFS (DFS$_\textrm{bi}$) has almost-fair \disj{} and unfair 
\conj{}. The implementation of DFS$_\textrm{bi}$ differs from DFS$_\textrm{i}$ 
in the \disj{} macro. We list the new \disj{} with its helper in 
Fig.~\ref{balanced-disj}. The helper \texttt{disj+} builds a balanced binary 
tree 
whose leaves are the goals and whose nodes are \texttt{disj2}, hence the name 
of 
this search strategy. The first argument 
to \texttt{disj+} is the goals. And the next two arguments accumulate goals in 
the left and right subtrees. The first clause says that when there is one goal, 
the tree is the goal itself. When there is more goals, they are partitioned 
into two sub-lists. The partition is done by repetitively dispatch the first 
two goals (the last clause), until no goal remains (the second clause) or one 
goal remains (the third clause). In contrast, the \disj{} in DFS$_\textrm{i}$ 
constructs the binary tree with the same collection of leaf nodes but in a 
particularly unbalanced form.
